--- 
title: "Kaggle Home Credit Default Risk"
author: "Fan Fei Chong<br><small>Advanced Analytics<br>Arch Capital Services Inc.</small>"
date: "<small>`r Sys.Date()`</small>"
output:
  html_document:
    toc: yes
    toc_depth: 3
    number_sections: true
    toc_float: 
      collapsed: false
    code_folding: hide
    theme: cerulean
css: stewarttoc.css
description: "some description ..."
---
<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" onclick="toggletoc()"><span>Outline</span></button>

<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>

```{r setup,echo=FALSE}
require(Hmisc)    # provides knitrSet and other functions
knitrSet(lang='markdown', fig.path='png/', fig.align='left', w=6.5, h=4.5, cache=TRUE)
# If using blogdown: knitrSet(lang='blogdown')

```

# Read in the data 
```{r data input, results='asis'}
library(data.table)
train_path <- "S:/ACTUARY3/Advanced Analytics/Private/Staff/Chong, Fan Fei/arch_kaggle_data/out/train_weighted.csv"
train = read.csv(train_path, stringsAsFactors= T, na.strings=".")
valid_path <- "S:/ACTUARY3/Advanced Analytics/Private/Staff/Chong, Fan Fei/arch_kaggle_data/out/valid_weighted.csv"
valid = read.csv(valid_path, stringsAsFactors= T, na.strings=".")
test_path <- "S:/ACTUARY3/Advanced Analytics/Private/Staff/Chong, Fan Fei/arch_kaggle_data/in/application_test.csv"
test = read.csv(test_path, stringsAsFactors= T)

library(dplyr)
library(rms)
library(Hmisc)
```

# Automatically generate a saturated model (symbolically)
```{r symbol_form}
M = train

col_set = M %>% names()
col_set = col_set[!col_set %in% "TARGET"]

string_formula = "TARGET~"
for(i in col_set){
  if(class(M[[i]]) == "numeric"){
    tmp_component = paste0("+rcs(",i,",3)")
  }
  if(class(M[[i]]) != "numeric"){
    tmp_component = paste0("+",i)
  }
  string_formula = paste0(string_formula, tmp_component)  
}
requested_formula = as.formula(string_formula)
requested_formula
```

# Prelim Model with no missing value imputation
```{r prelim, results='asis'}
# would work
string_formula <- TARGET ~ NAME_CONTRACT_TYPE + CODE_GENDER + FLAG_OWN_CAR + rcs(EXT_SOURCE_1, 4) + rcs(EXT_SOURCE_2, 4) + rcs(EXT_SOURCE_3, 4)
requested_formula = as.formula(string_formula)
a_model = lrm(data=M, formula = requested_formula, weight=weight, x=TRUE, y=TRUE)
library(pander)
a_model
```
A really basic model because of the extensive missing values, If we add an additional variable AMT_CREDIT, there would be so much case deletion that the model won't even be fitted at all. Error Message:

(singular information matrix in lrm.fit (rank= 9 ).  Offending variable(s): EXT_SOURCE_3' EXT_SOURCE_2' EXT_SOURCE_1' )

```{r not_work, results='asis2'}
# Model that did not work 
# would not work
#string_formula <- TARGET ~ NAME_CONTRACT_TYPE + CODE_GENDER + FLAG_OWN_CAR + rcs(EXT_SOURCE_1, 3) + rcs(EXT_SOURCE_2, 3) + rcs(EXT_SOURCE_3, 3)+ 
#  rcs(AMT_CREDIT, 3)
# requested_formula = as.formula(string_formula)
# a_model = lrm(data=M, formula = requested_formula, weight=weight)
```

## Use the fitted model to score a dataset
```{r relate}
valid_scored <- cbind(valid, predict(a_model, valid, se.fit=TRUE))
test_scored <- cbind(test, predict(a_model, test, se.fit=TRUE))
head(test_scored$linear.predictors)
```
Showing the first 5 predicted log-odds on the test set.
We see that without imputing the missing values for the predictors, we would have missing in our prediction.

## Diagnostic plots
### Variable Importance
```{r var_imp, cap="Variable Importance, in order of Chi-square statistics"}
plot(anova(a_model))
```

### Partial Effect Plot
```{r part_eff}
dd <- datadist(train); options(datadist='dd')
ggplot(Predict(a_model),sepdiscrete='vertical',vnames='names')#,
       #rdata=train,histSpike.opts=list(frac=function(f) .1*
        #                                 f/max(f)))
```

### Validation Statistics
```{r valid}
validate(a_model, B=100)
```

### Weighted ROC
```{r ROC}
# create artificial scores as random numbers
# x <- rnorm( 1000 );
# y <- rnorm( 1000, -1 );
# create artificial weights
# x.weights <- runif( 1000 );
# y.weights <- runif( 1000 );
# compute ROC curve and area under curve
# roc <- roc.curve( x, y, x.weights, y.weights, curve = TRUE );
```

### Calibration Curve
```{r calibrate}
plot(calibrate(a_model, B=100))
```
We see that only 8719 out of 24575 observations are used. Missing out a lot.

# Handling Missing Values
## Check out missing patterns
```{r missing}
na.patterns <- naclus(train)
require(rpart)
who.na <- rpart(is.na(EXT_SOURCE_1) ~ . - EXT_SOURCE_1, data=train,minbucket=15)
naplot(na.patterns, 'na per var')
plot(who.na, margin = .1); text(who.na)
#plot(na.pattterns)
```
